%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Alex McKinnon - Resume
% 
%
% Based on Hieu Do - Resume
% 2016/7/26
%
% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Alex McKinnon}
{\urlstyle{same}
	\faEnvelope \href{mailto:alex@mckinnon.io}{ alex@mckinnon.io}\\
    %\faGlobe \href{https://mckinnon.io}{ mckinnon.io}\\
	\faGithub \href{https://github.com/alexjmck}{   github.com/alexjmck}\\
	\faLinkedinSquare \href{https://www.linkedin.com/in/alex-mckinnon}{   /in/alex-mckinnon}
}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.3\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{Queen's University}
\descript{BASc in Computer Engineering Candidate}
Software Engineering Stream \\
Expected Grad. May 2021 \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Programming}
\location{Experienced:}
C++, Java, Unix Bash\\ 
\location{Moderate:}
MATLAB, Arduino, Nios II Assembly, VHDL\\ 
\sublocation{Beginner:}
Swift, \TeX

\subsection{Web Technologies:}
HTML5, CSS \\

\subsection{Tools:}
Cygwin, Eclipse, Visual Studio, 
Xcode, Adobe Lightroom, 
Photoshop, Premiere, \\
After Effects, MS Office \\ 

% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, Vietnamese\\
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     HACKATHONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Hackathons}
% HackMIT \textbullet{} hackNY \\
% WearHacks NY \textbullet{} Hackademics VN \\
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
Entrepreneurship Foundations,\\
Intro to Canadian Law,\\
Engineering Economics,\\
Engineering Design and Practice,\\
Computer Architecture, \\
Data Structures \& Algorithms,\\
Digital Systems,\\
Discrete Mathematics, \\
Machine Vision,\\
Probability,\\
Software Quality Assurance\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards}
Duke of Edinburgh Silver Level,\\
Alexander Rutherford Scholarship, \\
Lang Family Scholarship, \\
Ray Kingsmith Scholarship \\
\sectionsep

\sectionsep
\DTMsetdatestyle{mylastupdate}
Last updated \DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Project EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Project Experience}

\workplace{CTRLGate Software Startup}{September 2017 – September 2018} \\
\position{Co-founder}{Kingston, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Co-founded a start up company focused on providing campus access control software for gated communities.
\item Approached and on-boarded to an incubator program at the Queen's University Innovation Center.
\item Built up a diverse advisory board while learned the ins and outs of starting a business in the tech \& security sector.
\end{tightemize}
\sectionsep

\workplace{Queen's Satellite Design Team}{Sept 2017 – February 2018}\\
\position{RF Communications Team Member}{Kingston, ON}
%\vspace{2em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Assisted with the development of the satellite's antennas communications system software.
\item Developed a better understanding of implementing comm systems on satellites for RF communications using the AX.25 protocol.
\end{tightemize}
\sectionsep

\workplace{Autonomous Targeting Defense System}{Jan 2017 – Apr 2017} \\
\position{Arduino Programming and Electronics}{Kingston, ON}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Assembled a motorized mount for a semi automatic paintball gun to be mounted onto a semi-autonomous sail boat.
\item Responsible for the electronics and responsible for the coding of the Arduino that controlled the mount.
\end{tightemize}
\sectionsep

%\workplace{Arabian Nights Musical Production}{Oct 2015 – Dec 2015} \\
%\position{Audio Engineer}{Calgary, AB}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Assisted with creating sound effects to be used in the musical.
%\item Responsible for setting up wireless mics for the cast and ensuring proper sound levels throughout the musical.
%\end{tightemize}
%\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}

\workplace{Engineering Society of Queen's University}{February 2018 – April 2019} \\
\position{Director of Communications}{Kingston, ON}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} 
\item Managed the communication channels of the Society.
\item Reported to the society's biweekly council.
\item Started an ongoing archiving project with the focus of publishing a publicly accessible archive of old society files and media.
\item Lead three content creation teams for production and promotion of the society, and one team for archiving society affairs and media.
\end{tightemize}
\sectionsep

\workplace{Engineering Society - I.T.}{Sept 2017 – April 2018}\\
\position{I.T. Support Coordinator}{Kingston, ON}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Responsible for managing the society's web server infrastructure ensuring the creation of new websites and constant uptime of $\approx 34$ other websites.
%\item Developing technical skills for work with servers (Linux server permissions, load balancing \& security).
\end{tightemize}
\sectionsep

%\workplace{Engineering Society Communications Team}{May 2017 – present} \\
%\position{Photography Manager}{Kingston, ON}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Delegating photography jobs to those most qualified on the team.
%\item Providing skill development resources to each team member.
%\end{tightemize}
%\sectionsep

\workplace{Uhaul Moving and Storage}{Jun 2017 – Aug 2017} \\
\position{Customer Service Representative}{Calgary, ON}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked directly with customers to rent trucks, equipment \& services that best suited their needs.
\item Qualified to perform level one \& two inspections on all trucks \& trailers.
\end{tightemize}
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     PROJECTS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Projects}
% \runsubsection{QSAT}
% \descript{}
% A web app that visualize texts by creating dynamic mind maps from users' input. Built with AngularJS using D3.js and Ace.
% \sectionsep

% \runsubsection{Autonomous Targeting Defense System}
% \descript{}
% \location{Best Software, Wearhacks NY 2015}
% An Android mobile and wearable app that recognizes hand gestures to send emergency alerts. Built with Java using Presto API.
% \sectionsep 

% \runsubsection{Sia}
% \descript{}
% \location{2nd Prize, Hackademics VN 2015}
% A pioneering sex-ed website that promotes sexuality and gender awareness among Vietnamese teenagers. Built with MEAN stack.
% \sectionsep

% \runsubsection{Imagely}
% \descript{}
% A web app that enhances language-learning experience by generating new words from pictures. Built with MEAN stack using Clarifai API and Yandex API.
% \sectionsep 

\end{minipage} 

\end{document}  
